---
title: "Behavioral Proximity Models & fMRI Activity Modulation"
author: "MW"
date: "`r Sys.Date()`"
output:
  pdf_document: default
---
# Proximity Results
### This file is to analyze MARCER data's proximity 
Notes: 
dACC parcel IDs: 
7Networks_LH_SalVentAttn_Med_1 P107
7Networks_LH_SalVentAttn_Med_2 P108
7Networks_LH_SalVentAttn_Med_4 P110
7Networks_RH_SalVentAttn_Med_1 P311
7Networks_RH_SalVentAttn_Med_2 P312
I plan to first look at them separately and then combine it all together. 
In the coged behavioral file, starting trial 46 is the first run of coged. 
```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())
#Packages
library(RNifti);library(boxr);
box_auth(); 
wustl.box <- TRUE;
library(lme4); library(knitr); library(rlang)
options(warnPartialMatchDollar=TRUE);   # safety option
fMRI.path <- "/scratch2/weie/COGED_CODE/np2_trial/np2trialwise/"
out.path <-"/scratch2/weie/COGED_CODE/np2_trial/np2analysis/"
atlas.path <- "/data/MARCER/ATLASES/";  
afni.path <- "/usr/local/pkg/afni_22/";   # path to the afni function executables
dir.desc <- "20230714test";  
sub.tbl <- read.table(paste0("/scratch2/weie/COGED_CODE/", dir.desc, "_subjectSet.txt"), stringsAsFactors=FALSE);
sub.ids <- sub.tbl$sub.id[which(sub.tbl$COGED_CatchNonCatch == TRUE)]
behavior.path <- box_ls('148056179835') 
time.ids <- c("eval","dm")
parcel.ids <- c(107,108,110,311,312)
```

```{r dataset, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
#Compile a dataset with all choice behavior, proximity, and fMRI activity
col.names <- c("subID","trial","RT","choice","Task","proximity","reward","eval.107","eval.108","eval.110","eval.311","eval.312","dm.107","dm.108","dm.110","dm.311","dm.312","eval.dACC","dm.dACC")
tbl.all <- array(NA,c(36*3*length(sub.ids), length(col.names)), dimnames=list(NULL,col.names))
tbl.all[,1] <- rep(sub.ids,each = 108)
tbl.all[,2] <- rep(1:108)
for (sid in 1:length(sub.ids)) { #sid <- 1
  file.name <- paste0("coged-MARCER-fMRI-",sub.ids[sid],"-converted.csv")
  file.id <- box_search(file.name)
  behavior.data <- box_read(file.id)
  tbl.all[((sid-1)*108+1):(108*sid),(3:7)] <- as.matrix(behavior.data[46:153,c("choiceRT","choice","hardTask","proximityValue","rewardAmount")])
  for (tid in 1:length(time.ids)) { # tid<-1
    fMRI.table <- read.delim(paste0(fMRI.path, "COGED_np2_trialwise_", time.ids[tid], "_sub", sub.ids[sid], ".txt"),header=FALSE)
    tbl.all[((sid-1)*108+1):(108*sid),(8+5*(tid-1)):(12+5*(tid-1))] <- as.matrix(fMRI.table[,parcel.ids])
    tbl.all[((sid-1)*108+1):(108*sid),(18+tid-1)] <- apply(fMRI.table[,parcel.ids], 1, mean, na.rm=TRUE)
  }
}
write.table(tbl.all,file = paste0(out.path, "COGED_trialwise_data.txt"), sep = "\t", row.names = FALSE, col.names = TRUE)

# # We need to mutate: 
# WM.coged.fmri %>% filter(trial > 45) %>% filter(choice != 9) %>%
#   mutate(choseHard = if_else((choice == 1), 0, 1), #choose 1 is easy, choose 2 is hard, choose 9 is NA

```


```{r choice_activity, warning=FALSE, message=FALSE}
# Behavioral choice model
data <- read.delim(paste0(out.path, "COGED_trialwise_data.txt"), header = TRUE)
library(tidyverse)
install.packages("tidyverse")
behavior <- data[data$choice !=9, ] 
behavior$choiceCode <- ifelse(behavior$choice ==1, 1, 0) #1 is choosing easy, 2 is choosing hard. So after recoding, 1 is easy, 0 is hard.
  mutate (choiceCode = if_else(choice == 1, 1, 0),
         loadCode = factor(Task, levels = c(1,2,3), labels = c(-1,0,1)),
         rewardCode = factor(reward, levels = c(2,3,4), labels = c(-1,0,1)))
behavior$loadCode <- as.numeric(as.character(behavior$loadCode))
behavior$rewardCode <- as.numeric(as.character(behavior$rewardCode))

dm~proximity+(1|PID)
choice~eval+dm+proximity+Task+Reward+(1|PID)
```


## Choice Behavior as a function of proximity
### Working Memory

```{r WM_bx_Prox, warning=F, message=F}
#clean data frame with Cog-ED choice behavior
##working memory
d.coged.wm <- coged.wm %>% select(subID, trial, choice, proximityValue, rewardAmount, hardTask) %>% filter(trial > 45) %>%
  filter(choice != 9) %>%
  mutate(choiceCode = if_else(choice == 1, 1, 0),
         Domain = "WM",
         loadCode = factor(hardTask, levels = c(1,2,3), labels = c(-1,0,1)),
         rewardCode = factor(rewardAmount, levels = c(2,3,4), labels = c(-1,0,1)))
d.coged.wm$loadCode <- as.numeric(as.character(d.coged.wm$loadCode))
d.coged.wm$rewardCode <- as.numeric(as.character(d.coged.wm$rewardCode))
#choice model
m.wm.prox.choice <- glmer(data = d.coged.wm, choiceCode ~ proximityValue + rewardCode + loadCode + (proximityValue|subID), family = "binomial")
summary(m.wm.prox.choice)
wm.prox.choice <- coef(m.wm.prox.choice)
wm.prox.choice.slopes <- wm.prox.choice[["subID"]] %>% rownames_to_column(var = "subID") %>% rename(proxSlope = proximityValue)
wm.prox.choice.slopes$subID <- as.numeric(wm.prox.choice.slopes$subID)
#creating SV variable
wm.SV <- wm.prox.choice.slopes %>%
  mutate(SV = -1*(`(Intercept)`/proxSlope))
kable(wm.SV)
```

### Speech

```{r SP_bx_Prox, warning=FALSE, message=FALSE}
##speech
d.coged.speech <- coged.speech %>% select(subID, trial, choice, proximityValue, rewardAmount, hardTask) %>%
  filter(trial > 45) %>% filter(choice != 9) %>%
  mutate(choiceCode = if_else(choice == 1, 1, 0),
         Domain = "SP",
         loadCode = factor(hardTask, levels = c(1,2,3), labels = c(-1,0,1)),
         rewardCode = factor(rewardAmount, levels = c(2,3,4), labels = c(-1,0,1)))
d.coged.speech$loadCode <- as.numeric(as.character(d.coged.speech$loadCode))
d.coged.speech$rewardCode <- as.numeric(as.character(d.coged.speech$rewardCode))
#choice model
m.sp.prox.choice <- glmer(data = d.coged.speech, choiceCode ~ proximityValue + rewardCode + loadCode + (proximityValue|subID), family = "binomial")
summary(m.sp.prox.choice)
sp.prox.choice <- coef(m.sp.prox.choice)
sp.prox.choice.slopes <- sp.prox.choice[["subID"]] %>% rownames_to_column(var = "subID") %>% rename(proxSlope = proximityValue)
sp.prox.choice.slopes$subID <- as.numeric(sp.prox.choice.slopes$subID)
#creating SV variable
sp.SV <- sp.prox.choice.slopes %>%
  mutate(SV = -1*(`(Intercept)`/proxSlope))
kable(sp.SV)
```

### Both Working Memory & Speech

```{r bx_Prox, warning=FALSE, message=FALSE}
#combining estimates into a single model across both domains
d.coged <- rbind(d.coged.wm, d.coged.speech) %>%
  mutate(domainCode = factor(Domain, levels = c("WM","SP"), labels = c(0,1)),
         loadCode = factor(hardTask, levels = c(1,2,3), labels = c(-1,0,1)),
         rewardCode = factor(rewardAmount, levels = c(2,3,4), labels = c(-1,0,1)))
d.coged$domainCode <- as.numeric(as.character(d.coged$domainCode))
d.coged$loadCode <- as.numeric(as.character(d.coged$loadCode))
d.coged$rewardCode <- as.numeric(as.character(d.coged$rewardCode))

#choice model
m.prox.choice <- glmer(data = d.coged, choiceCode ~ proximityValue + domainCode + rewardCode + loadCode + (proximityValue|subID), family = "binomial")
summary(m.prox.choice)
prox.choice <- coef(m.prox.choice)
prox.choice.slopes <- prox.choice[["subID"]] %>% rownames_to_column(var = "subID") %>% rename(proxSlope = proximityValue)
prox.choice.slopes$subID <- as.numeric(prox.choice.slopes$subID)
#creating SV variable
d.SV <- prox.choice.slopes %>%
  mutate(SV = -1*(`(Intercept)`/proxSlope))
kable(d.SV)
```

# fMRI Proximity modulation

```{r prox, warning=FALSE, message=FALSE}
#N-Back Cog-ED
nback.sph <- nback.spheres %>% rename("region" = cifti.name) %>%
  group_by(subID, tent, region) %>%
  mutate(tent = tent+1) %>% group_by(tent, condition, region) %>%
  summarise(meanValue = mean(value))

nback.sph.prox <- nback.spheres %>% filter(condition == "valProx") %>% rename("region" = cifti.name) %>%
  group_by(subID, tent, region) %>%
  mutate(tent = tent+1) %>%
  summarise(meanValue = mean(value)) %>% mutate(Domain = "WM")

nback.sph.meanResp <- nback.spheres %>% filter(condition == "meanResp") %>% rename("region" = cifti.name) %>%
  group_by(subID, tent, region) %>%
  mutate(tent = tent+1) %>%
  summarise(meanValue = mean(value)) %>% mutate(Domain = "WM")

speech.sph <- speech.spheres %>% rename("region" = cifti.name) %>%
  group_by(subID, tent, region) %>%
  mutate(tent = tent+1) %>% group_by(tent, condition, region) %>%
  summarise(meanValue = mean(value))

speech.sph.prox <- speech.spheres %>% filter(condition == "valProx") %>% rename("region" = cifti.name) %>%
  group_by(subID, tent, region) %>%
  mutate(tent = tent+1) %>%
  summarise(meanValue = mean(value)) %>% mutate(Domain = "SP")

speech.sph.meanResp <- speech.spheres %>% filter(condition == "meanResp") %>% rename("region" = cifti.name) %>%
  group_by(subID, tent, region) %>%
  mutate(tent = tent+1) %>%
  summarise(meanValue = mean(value)) %>% mutate(Domain = "SP")

sph.prox <- rbind(nback.sph.prox, speech.sph.prox)
sph.prox.dACC.dmPFC <- sph.prox %>% filter(region == "dACC"|region == "dmPFC") %>% filter(tent == 6)
sph.meanResp <- rbind(nback.sph.meanResp, speech.sph.meanResp)
```

### Proximity modulation and behavioral choice patterns
### dACC

```{r prox_dACC_choice, warning=FALSE, message=FALSE}
#tent 6
prox.Tent6.dACC<- sph.prox %>% filter(tent == 6) %>% filter(region %in% c("dACC")) %>%
  group_by(subID) %>% summarise(meanValue = mean(meanValue))

prox.chc.fMRI <- inner_join(prox.choice.slopes, prox.Tent6.dACC)

#Correlations between proximity modulation and behavioral choice patterns
##Tent 6
dACC.prox.cor <- cor_test(data = prox.chc.fMRI, x = "meanValue", y = "proxSlope")
dACC.prox.cor

#plot
prox.cor <- visualisation_recipe(dACC.prox.cor, labs = list(x = "dACC Proximity Modulation", y = "Proximity Slope"))
p.prox.cor.dacc <- plot(prox.cor) + theme_classic() + labs(title = "Both Working Memory & Speech Domains")
p.prox.cor.dacc

#working memory
#tent 6
wm.prox.Tent6.dACC<- nback.sph.prox %>% filter(tent == 6) %>% filter(region %in% c("dACC")) %>%
  group_by(subID) %>% summarise(meanValue = mean(meanValue))

wm.prox.chc.fMRI <- inner_join(wm.prox.choice.slopes, wm.prox.Tent6.dACC)

#Correlations between proximity modulation and behavioral choice patterns
##Tent 6
dACC.wm.prox.cor <- cor_test(data = wm.prox.chc.fMRI, x = "meanValue", y = "proxSlope")
dACC.wm.prox.cor

#plot
wm.prox.cor <- visualisation_recipe(dACC.wm.prox.cor, labs = list(x = "dACC Proximity Modulation", y = "Proximity Slope"))
p.wm.prox.cor <- plot(wm.prox.cor) + theme_classic() + labs(title = "Working Memory Domain")
p.wm.prox.cor

#speech
#tent 6
sp.prox.Tent6.dACC<- speech.sph.prox %>% filter(tent == 6) %>% filter(region %in% c("dACC")) %>%
  group_by(subID) %>% summarise(meanValue = mean(meanValue))

sp.prox.chc.fMRI <- inner_join(sp.prox.choice.slopes, sp.prox.Tent6.dACC)

#Correlations between proximity modulation and behavioral choice patterns
##Tent 6
dACC.sp.prox.cor <- cor_test(data = sp.prox.chc.fMRI, x = "meanValue", y = "proxSlope")
dACC.sp.prox.cor

#plot
sp.prox.cor <- visualisation_recipe(dACC.sp.prox.cor, labs = list(x = "dACC Proximity Modulation", y = "Proximity Slope"))
p.sp.prox.cor <- plot(sp.prox.cor) + theme_classic() + labs(title = "Speech Domain")
p.sp.prox.cor
```

### dmPFC

```{r prox_dmPFC_choice, warning=FALSE, message=FALSE}
#tent 6
prox.Tent6.dmPFC<- sph.prox %>% filter(tent == 6) %>% filter(region %in% c("dmPFC")) %>%
  group_by(subID) %>% summarise(meanValue = mean(meanValue))

prox.chc.fMRI <- inner_join(prox.choice.slopes, prox.Tent6.dmPFC)

#Correlations between proximity modulation and behavioral choice patterns
##Tent 6
dmPFC.prox.cor <- cor_test(data = prox.chc.fMRI, x = "meanValue", y = "proxSlope")
dmPFC.prox.cor

#plot
prox.cor <- visualisation_recipe(dmPFC.prox.cor, labs = list(x = "dmPFC Proximity Modulation", y = "Proximity Slope"))
p.prox.cor.dmpfc <- plot(prox.cor) + theme_classic() + labs(title = "Both Working Memory & Speech Domains")
p.prox.cor.dmpfc

#working memory
#tent 6
wm.prox.Tent6.dmPFC<- nback.sph.prox %>% filter(tent == 6) %>% filter(region %in% c("dmPFC")) %>%
  group_by(subID) %>% summarise(meanValue = mean(meanValue))

wm.prox.chc.fMRI <- inner_join(wm.prox.choice.slopes, wm.prox.Tent6.dmPFC)

#Correlations between proximity modulation and behavioral choice patterns
##Tent 6
dmPFC.wm.prox.cor <- cor_test(data = wm.prox.chc.fMRI, x = "meanValue", y = "proxSlope")
dmPFC.wm.prox.cor

#plot
wm.prox.cor <- visualisation_recipe(dmPFC.wm.prox.cor, labs = list(x = "dmPFC Proximity Modulation", y = "Proximity Slope"))
p.wm.prox.cor <- plot(wm.prox.cor) + theme_classic() + labs(title = "Working Memory Domain")
p.wm.prox.cor

#speech
#tent 6
sp.prox.Tent6.dmPFC<- speech.sph.prox %>% filter(tent == 6) %>% filter(region %in% c("dmPFC")) %>%
  group_by(subID) %>% summarise(meanValue = mean(meanValue))

sp.prox.chc.fMRI <- inner_join(sp.prox.choice.slopes, sp.prox.Tent6.dmPFC)

#Correlations between proximity modulation and behavioral choice patterns
##Tent 6
dmPFC.sp.prox.cor <- cor_test(data = sp.prox.chc.fMRI, x = "meanValue", y = "proxSlope")
dmPFC.sp.prox.cor

#plot
sp.prox.cor <- visualisation_recipe(dmPFC.sp.prox.cor, labs = list(x = "dmPFC Proximity Modulation", y = "Proximity Slope"))
p.sp.prox.cor <- plot(sp.prox.cor) + theme_classic() + labs(title = "Speech Domain")
p.sp.prox.cor
```

## Adding dmPFC and dACC activity into logistic regression model predicting choice 

```{r choice_fMRI, message=FALSE, warning=FALSE}
d.coged.fmri <- d.coged %>% inner_join(sph.prox.dACC.dmPFC)
d.coged.fmri.dACC <- d.coged.fmri %>% filter(region == "dACC")
d.coged.fmri.dmPFC <- d.coged.fmri %>% filter(region == "dmPFC")

#choice model--dACC
m.prox.choice.dACC <- glmer(data = d.coged.fmri.dACC, choiceCode ~ proximityValue + domainCode + rewardCode + loadCode + meanValue + (proximityValue|subID), family = "binomial")
summary(m.prox.choice.dACC)

#choice model--dmPFC
m.prox.choice.dmPFC <- glmer(data = d.coged.fmri.dmPFC, choiceCode ~ proximityValue + domainCode + rewardCode + loadCode + meanValue + (proximityValue|subID), family = "binomial")
summary(m.prox.choice.dmPFC)





```