---
title: "MARCER Proximity Models & fMRI Activity Modulation"
author: "Mengzhe Wei"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    toc: yes
    toc_float:
      collapsed: true
---

# MARCER COGED fMRI Results
#### There are 143 participants that have completed scan session. 142 participants have at least some coged/nback in lab data (7306 was excluded due to not completing any coged/nback in and out of the scanner despite having IAPS data). 134 participants have at least some COGED scan data.
#### N.b. all error bars in this summary are 95% CIs

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())
library(lme4); library(tidyverse)
fMRI.path <- "C:/Users/Emotion/Documents/GIT-MW/COG-ED/Data/TrialData/"
demo <- read.csv("C:/Users/Emotion/Documents/GIT-MW/COG-ED/Data/BehaviorData/demo.csv")
# Clean up model
data <- read.delim(paste0(fMRI.path,"COGED_trialwise_data_sphere_5-7.txt"), header = TRUE)
data.clean <- data %>%
  left_join(demo %>% select(sub.id, MDD_Status, Age), by = c("subID" = "sub.id")) %>%
  filter(choice !=9) %>%
  mutate (choiceCode = if_else((choice == 1), 0, 1), #1 is choosing easy, 2 is choosing hard. So after recoding, 0 is easy, 1 is hard. As proximity goes higher, people should be more biased to choose the harder option.
          loadCode = factor(hardTask, levels = c(1,2,3), labels = c(-1,0,1)),
          rewardCode = factor(rewardAmount, levels = c(2,3,4), labels = c(-1,0,1)),
          groupCode = factor (MDD_Status, levels = c("HC", "MDD"), labels = c(0,1)),
          Age_centered = scale(Age, center = TRUE, scale = FALSE),
          eval_vmPFC = rowMeans(select(., eval_vmPFC_right_LG, eval_vmPFC_left_LG, eval_vmPFC_right_Bartra), na.rm = TRUE),
          eval_VS = rowMeans(select(., eval_VS_right, eval_VS_left), na.rm = TRUE),
          dm_AI = rowMeans(select(., dm_AI_left, dm_AI_right,dm_AI_right_Chong), na.rm = TRUE),
          dm_IPL = rowMeans(select(., dm_IPL_left_1,dm_IPL_left_2), na.rm = TRUE))
data.clean$loadCode <- as.numeric(as.character(data.clean$loadCode))
data.clean$rewardCode <- as.numeric(as.character(data.clean$rewardCode))
data.clean$Age <- as.numeric(as.character(data.clean$Age))
data.clean$groupCode <- as.numeric(as.character(data.clean$groupCode))
data.clean$subID <-  as.factor(data.clean$subID)

data.clean <- data.clean %>%
  mutate(Age_centered = scale(Age, center = TRUE, scale = FALSE))
```

#### Behavior check
```{r Behavior, warning=FALSE, message=FALSE}
# Behavioral choice model 
prox.choice <- glmer(data = data.clean, choiceCode ~ proximityValue + rewardCode + loadCode + (proximityValue|subID), family = "binomial")
summary(prox.choice) #As expected, the higher the proximity, the more likely people are to choose the harder option. The higher the reward for the harder option, the more likely people are to choose the harder option (p = 0.004). The higher the load of the hard task is, the less likely people are to choose the easier option. 
library(easystats)
prox.choice.plot <- get_datagrid(prox.choice, by = c("proximityValue","subID"), preserve_range = TRUE)
preds <- estimate_relation(prox.choice, include_random = T, data = prox.choice.plot)

prox.choice.plot.fixed <- get_datagrid(prox.choice, by = c("proximityValue"), preserve_range = TRUE)
fixed_pred <- estimate_relation(prox.choice, at = "proximityValue", data = prox.choice.plot.fixed)

fig1 <- ggplot(fixed_pred, aes(x=proximityValue, y=Predicted)) + 
  geom_ribbon(data = fixed_pred, aes(x = proximityValue, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = fixed_pred, aes(x = proximityValue, y = Predicted), linewidth = 2) +
  geom_line(data = preds, aes(x=proximityValue, y=Predicted, group=subID, colour = factor(subID)), alpha=0.5) + theme_classic() + labs(x= "Relative Subjective Value of High-Effort Option", y="Proabability of High-Effort Option")
fig.pt <- fig1 + guides(colour=FALSE) + geom_hline(yintercept = 0.5, linetype = "dashed") + 
  geom_vline(xintercept = 0, linetype = "dashed")
fig.pt
```

# Hypotheses testing

## H4: Task Load and Reward Effects  

Model:  Generalized linear mixed-effects model with neural activation in vmPFC, VS, vlPFC, and OFC as the dependent variable. 

**Predictors:** <br>
- Main effect of task load and reward load (H4a)  <br>
- Interaction between task load/reward load and age (H4b). <br>
- Interaction between task load/reward load and MDD status (H4c).  <br>
**ROI:** <br>
- vmPFC: sphere vmPFC_right_LG, vmPFC_left_LG, vmPFC_right_Bartra
- VS: sphere VS_left, VS_right
- vlPFC & OFC: not sure how to define yet; we eyeballed it in our whole brain schaefer 400 knitr
```{r H4, warning=F, message=F, cache=F}
# H4a: task load and reward load on vmPFC
vmPFC <- lmer(data = data.clean, eval_vmPFC ~ rewardCode + loadCode + groupCode + Age + (1 | subID))
summary(vmPFC) # task load and reward load doesn't predict vmPFC activity during evaluation phase
# H4a: task load and reward load on VS
VS <- lmer(data = data.clean, eval_VS ~ rewardCode + loadCode + groupCode + Age + (1 | subID))
summary(VS) # task load and reward load doesn't predict VS activity during evaluation phase, but age & depression predict higher activation

# H4b: Age interaction with task
vmPFC.age.task <- lmer(data = data.clean, eval_vmPFC ~ rewardCode + loadCode*Age + groupCode + (1 | subID))
summary(vmPFC.age.task) #no interaction
VS.age.task <- lmer(data = data.clean, eval_VS ~ rewardCode + loadCode*Age + groupCode + (1 | subID))
summary(VS.age.task) #no interaction

# H4b: Age interaction with reward
vmPFC.age.reward <- lmer(data = data.clean, eval_vmPFC ~ rewardCode*Age + loadCode + groupCode + (1 | subID))
summary(vmPFC.age.reward) #no interaction
VS.age.reward <- lmer(data = data.clean, eval_VS ~ rewardCode*Age + loadCode + groupCode + (1 | subID))
summary(VS.age.reward) #reward is associated with greater VS activation; older age is associated with greater VS activation;positive effect of reward on VS activation decreases with age.

# H4c: MDD interaction with task
vmPFC.MDD.task <- lmer(data = data.clean, eval_vmPFC ~ rewardCode + loadCode*groupCode + Age + (1 | subID))
summary(vmPFC.MDD.task) #no interaction
VS.MDD.task <- lmer(data = data.clean, eval_VS ~ rewardCode + loadCode*groupCode + Age + (1 | subID))
summary(VS.MDD.task) #no interaction

# H4c: MDD interaction with reward
vmPFC.MDD.reward <- lmer(data = data.clean, eval_vmPFC ~ rewardCode*groupCode + loadCode + Age + (1 | subID))
summary(vmPFC.MDD.reward) #no interaction
VS.MDD.reward <- lmer(data = data.clean, eval_VS ~ rewardCode*groupCode + loadCode + Age + (1 | subID))
summary(VS.MDD.reward) #no interaction

#Exploratory: MDD and age interaction
vmPFC.age.MDD.task <- lmer(data = data.clean, eval_vmPFC ~ loadCode*groupCode*Age + rewardCode + (1 | subID))
summary(vmPFC.age.MDD.task) #NS
vmPFC.age.MDD.reward <- lmer(data = data.clean, eval_vmPFC ~ rewardCode*groupCode*Age + loadCode + (1 | subID))
summary(vmPFC.age.MDD.reward)#NS
VS.age.MDD.task <- lmer(data = data.clean, eval_VS ~ loadCode*groupCode*Age + rewardCode + (1 | subID))
summary(VS.age.MDD.task)#NS
VS.age.MDD.reward <- lmer(data = data.clean, eval_VS ~ rewardCode*groupCode*Age + loadCode + (1 | subID))
summary(VS.age.MDD.reward)#NS
```

## H5: Proximity Effects on Neural Activities 

Model:  Generalized linear mixed-effects model with dACC and dmPFC activation as the dependent variable. 

**Predictors:** <br>
- Main effect of proximity  (H5a)  <br>
- Interaction between proximity and age (H5b). <br>
- Interaction between proximity and MDD status (H5c).  <br>
**ROI:** <br>
- dACC: sphere dACC
- dmPFC: sphere dmPFC
```{r H5, warning=F, message=F, cache=F}
# H5a: proximity on dACC activation during decision making phase
dACC <- lmer(data = data.clean, dm_dACC ~ proximityValue + groupCode + Age + (proximityValue | subID))
summary(dACC) # same direction but not significant, age has a negative main effect of dACC activation

dacc.fig.data <- get_datagrid(dACC, by = c("proximityValue","subID"), preserve_range = TRUE)
dacc.fig.data.fixed <- get_datagrid(dACC, by = c("proximityValue"), preserve_range = TRUE)
preds <- estimate_relation(dACC, include_random = T, data = dacc.fig.data)
fixed_pred <- estimate_relation(dACC, at = "proximityValue", data = dacc.fig.data.fixed)
fig.dACC <- ggplot(fixed_pred, aes(x=proximityValue, y=Predicted)) + 
  geom_ribbon(data = fixed_pred, aes(x = proximityValue, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = fixed_pred, aes(x = proximityValue, y = Predicted), linewidth = 2) +
  geom_line(data = preds, aes(x=proximityValue, y=Predicted, group=subID, colour = factor(subID)), alpha=0.5) + theme_classic() + labs(x= "Relative Subjective Value", y="dACC Activity") + ylim(-0.005,0.02)
dacc.fig <- fig.dACC + guides(colour=FALSE)
dacc.fig

# H5a: proximity on dmPFC
dmPFC <- lmer(data = data.clean, dm_dmPFC ~ proximityValue + groupCode + Age + (proximityValue | subID))
summary(dmPFC) # N.S., age has a negative main effect of dACC activation

# H5b: Age interaction on dACC
dACC.age <- lmer(data = data.clean, dm_dACC ~ proximityValue*Age + groupCode + (proximityValue | subID))
summary(dACC.age) #no interaction
# H5b: Age interaction on dmPFC
dmPFC.age <- lmer(data = data.clean, dm_dmPFC ~ proximityValue*Age + groupCode + (proximityValue | subID))
summary(dmPFC.age) #no interaction

# H5c: MDD interaction on dACC
dACC.MDD <- lmer(data = data.clean, dm_dACC ~ proximityValue*groupCode + Age + (proximityValue | subID))
summary(dACC.MDD) #no interaction
# H5c: MDD interaction on dmPFC
dmPFC.MDD <- lmer(data = data.clean, dm_dmPFC ~ proximityValue*groupCode + Age + (proximityValue | subID))
summary(dmPFC.MDD) #no interaction

#Exploratory: MDD & Age interaction
dACC.age.MDD <- lmer(data = data.clean, dm_dACC ~ proximityValue*Age*groupCode + (proximityValue | subID))
summary(dACC.age.MDD)
dmPFC.age.MDD <- lmer(data = data.clean, dm_dmPFC ~ proximityValue*Age*groupCode + (proximityValue | subID))
summary(dmPFC.age.MDD)
```

## H6:  Mediation of Relative SV and Choice Behavior (if H5a tested significant); H5a was insignificant, so only look at activation and choice behavior

Model: Multilevel mediation analysis using dACC and dmPFC activation as predictors of choice behavior

**Predictors:** <br>
- Main effect of dACC and dmPFC activation  (H6a)  <br>
- Interaction between dACC, dmPFC activation and age (H6b). <br>
- Interaction between dACC, dmPFC activation and MDD status (H6c).  <br>
**ROI:** <br>
- dACC: sphere dACC
- dmPFC: sphere dmPFC
```{r H6, warning=F, message=F, cache=F}
# H6a: dACC activation during decision making phase on choice behavior
dACC <- glmer(data = data.clean, choiceCode ~ dm_dACC + groupCode + Age + (1 | subID),family = "binomial")
summary(dACC) # NS

# H6a: dmPFC activation during decision making phase on choice behavior
dmPFC <- glmer(data = data.clean, choiceCode ~ dm_dmPFC + groupCode + Age + (1 | subID),family = "binomial")
summary(dmPFC) # N.S.

# H6b: Age interaction on dACC
dACC.age <- glmer(data = data.clean, choiceCode ~ dm_dACC*Age_centered + groupCode + (1 | subID),family = "binomial")
summary(dACC.age) #higher dm_dacc, higher chance of choosing the harder option. That effect is stronger in older adults (marginally significant)
# H6b: Age interaction on dmPFC
dmPFC.age <- glmer(data = data.clean, choiceCode ~ dm_dmPFC*Age_centered + groupCode + (1 | subID), family = "binomial")
summary(dmPFC.age) #the association between dm_dmPFC and choosing the harder option is stronger in older adults.

# H6c: MDD interaction on dACC
dACC.MDD <- glmer(data = data.clean, choiceCode ~ dm_dACC*groupCode + Age_centered + (1 | subID),family = "binomial")
summary(dACC.MDD) #no interaction
# H6c: MDD interaction on dmPFC
dmPFC.MDD <- glmer(data = data.clean, choiceCode ~ dm_dmPFC*groupCode + Age_centered + (1 | subID),family = "binomial")
summary(dmPFC.MDD) #no interaction

#Exploratory: MDD & Age interaction
dACC.age.MDD <- glmer(data = data.clean, choiceCode ~ dm_dACC*Age_centered*groupCode + (1 | subID),family = "binomial")
summary(dACC.age.MDD)
dmPFC.age.MDD <- glmer(data = data.clean, choiceCode ~ dm_dmPFC*Age_centered*groupCode + (1 | subID),family = "binomial")
summary(dmPFC.age.MDD)
```

## H7:  Decision Difficulty Proximity^2 on Neural Activity 

Model: Generalized linear mixed-effects model predicting neural activation in AI and IPL as a function of proximity². 

**Predictors:** <br>
- Main effect of proximity² (H7a)  <br>
- Interaction between proximity and age (H7b). <br>
- Interaction between proximity and MDD status (H7c).  <br>
- Covariate: RT <br>
**ROI:** <br>
- AI: sphere AI
- IPL: sphere IPL
```{r H7, warning=F, message=F, cache=F}
# H7a: proximity^2 on AI activation
AI <- lmer(data = data.clean, dm_AI ~ I(proximityValue^2) + groupCode + Age + choiceRT + (I(proximityValue^2) | subID))
summary(AI) # higher the proximity^2 (easier the choice), higher the activation in AI

# H7a: proximity^2 on IPL activation
IPL <- lmer(data = data.clean, dm_IPL ~ I(proximityValue^2) + groupCode + Age + choiceRT + (I(proximityValue^2) | subID))
summary(IPL) # higher the proximity^2 (easier the choice), higher the activation in IPL

# H7b: Age interaction on AI
AI.age <- lmer(data = data.clean, dm_AI ~ I(proximityValue^2)*Age + groupCode + (I(proximityValue^2) | subID))
summary(AI.age) #NS
# H7b: Age interaction on IPL
IPL.age <- lmer(data = data.clean, dm_IPL ~ I(proximityValue^2)*Age + groupCode + (I(proximityValue^2) | subID))
summary(IPL.age) #NS

# H7c: MDD interaction on AI
AI.MDD <- lmer(data = data.clean, dm_AI ~ I(proximityValue^2)*groupCode + Age + (I(proximityValue^2) | subID))
summary(AI.MDD) #no interaction
# H7c: MDD interaction on IPL
IPL.MDD <- lmer(data = data.clean, dm_IPL ~ I(proximityValue^2)*groupCode + Age + (I(proximityValue^2) | subID))
summary(IPL.MDD) #no interaction

#Exploratory: MDD & Age interaction
AI.age.MDD <- lmer(data = data.clean, dm_AI ~ I(proximityValue^2)*groupCode*Age + (I(proximityValue^2) | subID))
summary(AI.age.MDD) #significant three way interaction

IPL.age.MDD <- lmer(data = data.clean, dm_IPL ~ I(proximityValue^2)*groupCode*Age + (I(proximityValue^2) | subID))
summary(IPL.age.MDD) #NS

age_mean <- mean(data.clean$Age, na.rm = TRUE)
age_sd <- sd(data.clean$Age, na.rm = TRUE)

# Generate the effect using Age at ±1 SD
ef <- effects::effect("I(proximityValue^2)*groupCode*Age", 
             mod = AI.age.MDD, 
             xlevels = list(Age = c(age_mean - age_sd, age_mean, age_mean + age_sd), groupCode =c(0,1) ))

# Convert to dataframe
efdata <- as.data.frame(ef)
efdata$groupCode <- as.factor(efdata$groupCode)

# Convert Age values into factor labels
efdata$Age <- factor(efdata$Age, 
                     levels = c(age_mean - age_sd, age_mean, age_mean + age_sd), 
                     labels = c("Low Age (-1 SD)", "Mean Age", "High Age (+1 SD)"))

# Plot the three-way interaction
ggplot(efdata, aes(x = I(proximityValue^2), y = fit, color = groupCode, group = groupCode)) + 
    geom_line(size = 1.2) +
    geom_ribbon(aes(ymin = fit - se, ymax = fit + se, fill = groupCode), alpha = 0.3) + 
    labs(x = "Proximity^2", y = "AI activation", 
         color = "groupCode", fill = "groupCode") +
    theme_classic() +
    facet_wrap(~ Age)
```