---
title: "COGED and IAPS Analysis"
author: "Mengzhe Wei, Chris Gu, Todd Braver"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    toc: yes
    toc_float:
      collapsed: true
---

# Cross-Subject Correlations in Cog-ED and IAPS
Notes: Started 16 Sep 2024 by Mengzhe Wei to run analysis looking at activities during COGED and IAPS. 

### Does the response to positive affect (LookPos-LookNeu) in IAPS correlate with the response to increasing reward amount in the CogED (Rew4-Rew2)? 
Does one's response in IAPS to predict their response in the CogED (scatterplot). Note that for CogED we are only looking at evaluation period in GLMs (3-5s), and for IAPS we are looking at GLM activity from 9s to 11s. 
Key ROIs:
vmPFC (https://doi.org/10.1016/j.neuropsychologia.2022.108303):
168	7Networks_LH_Default_PFC_3	
169	7Networks_LH_Default_PFC_4	
173	7Networks_LH_Default_PFC_8	
174	7Networks_LH_Default_PFC_9	
379	7Networks_RH_Default_PFCdPFCm_1
380	7Networks_RH_Default_PFCdPFCm_2
381	7Networks_RH_Default_PFCdPFCm_3
382	7Networks_RH_Default_PFCdPFCm_4
Ventral Striatum: Accumbens, Putamen

### Set up
```{r setup, eval=TRUE, echo=TRUE, warning=FALSE, message=FALSE}
#basic setup
rm(list=ls())
options(warnPartialMatchDollar=TRUE);   # safety option
library(RNifti); library(lme4); library(knitr); library(dplyr); #Packages
in.path <- "/scratch2/weie/COGED_CODE/MW+CG_IAPSCOGED/"
out.path <-"/scratch2/weie/COGED_CODE/MW+CG_IAPSCOGED/"
dir.desc <- "20230714test";  
sub.tbl <- read.table(paste0("/scratch2/weie/COGED_CODE/", dir.desc, "_subjectSet.txt"), stringsAsFactors=FALSE);
sub.ids <- sub.tbl$sub.id[which(sub.tbl$COGED_CatchNonCatch == TRUE)]
#select data needed for analysis
schaefer.parcel.ids <- c(168,169,173,174,379,380,381,382)
schaefer.parcel.ids <- paste0("p", schaefer.parcel.ids)
subcortical.parcel.ids <- c("accumbensL","accumbensR","putamenL","putamenR")
COGED <- read.delim(paste0(in.path, "COGED_Rew4_Rew2_Eval.txt"),header=TRUE)
IAPS <- read.delim(paste0(in.path, "IAPS_LookPos_LookNeu_9to11.txt"),header=TRUE)
COGED.ROI <-COGED[,c("subID", subcortical.parcel.ids, schaefer.parcel.ids)]
IAPS.ROI <-IAPS[,c("SubID", subcortical.parcel.ids, schaefer.parcel.ids)]  #little note to MW here, Chris capitalized subID.
colnames(IAPS.ROI)[colnames(IAPS.ROI) == "SubID"] <- "subID"
data <- merge(COGED.ROI, IAPS.ROI, by = "subID",suffixes = c("_rew", "_pos"))
data$vmpfc_rew <- apply(data[,paste0(schaefer.parcel.ids,"_rew")], 1, mean, na.rm=TRUE)
data$vmpfc_pos <- apply(data[,paste0(schaefer.parcel.ids,"_pos")], 1, mean, na.rm=TRUE)
```

### Scatter plot
```{r scatterplot, eval=TRUE, echo=TRUE, warning=FALSE, message=FALSE}
layout(matrix(1:15, 5,3, byrow=TRUE)); 
par(mar = c(2, 2, 2, 1), mgp = c(1.1, 0.2, 0), tcl = -0.3);

# loop through subcortical parcels
for (i in 1:length(subcortical.parcel.ids)) { #i<-1
  # Generate scatter plot for Schaefer parcels
  plot(
    data[[paste0(subcortical.parcel.ids[i], "_rew")]], 
    data[[paste0(subcortical.parcel.ids[i], "_pos")]], 
    xlab = "Rew4-Rew2", 
    ylab = "Pos-Neu", 
    main = subcortical.parcel.ids[i], 
    pch = 16, col = "darkgreen"
  )
  abline(lm(data[[paste0(subcortical.parcel.ids[i], "_rew")]]~data[[paste0(subcortical.parcel.ids[i], "_pos")]]))
}

# loop through schaefer parcels
for (i in 1:length(schaefer.parcel.ids)) { #i<-1
  # Generate scatter plot for Schaefer parcels
  plot(
    data[[paste0(schaefer.parcel.ids[i], "_rew")]], 
    data[[paste0(schaefer.parcel.ids[i], "_pos")]], 
    xlab = "Rew4-Rew2", 
    ylab = "Pos-Neu", 
    main = schaefer.parcel.ids[i], 
    pch = 16, col = "darkgreen"
  )
  abline(lm(data[[paste0(schaefer.parcel.ids[i], "_rew")]]~data[[paste0(schaefer.parcel.ids[i], "_pos")]]))
}

#Graph the one mega parcel
plot(
    data[["vmpfc_rew"]], 
    data[["vmpfc_pos"]], 
    xlab = "Rew4-Rew2", 
    ylab = "Pos-Neu", 
    main = "vmPFC mega parcel", 
    pch = 16, col = "darkgreen"
  )
abline(lm(data[["vmpfc_rew"]]~data[["vmpfc_pos"]]))
par(mfrow = c(1, 1))
```

### Regression
```{r regression, warning=FALSE, message=TRUE}
for (i in 1:length(subcortical.parcel.ids)) {
regression<-lm(data[[paste0(subcortical.parcel.ids[i], "_pos")]]~data[[paste0(subcortical.parcel.ids[i], "_rew")]])
message(paste0(subcortical.parcel.ids[i]), " simple linear regression model")
print(summary(regression))
}
for (i in 1:length(schaefer.parcel.ids)) {
regression<-lm(data[[paste0(schaefer.parcel.ids[i], "_pos")]]~data[[paste0(schaefer.parcel.ids[i], "_rew")]])
message(paste0(schaefer.parcel.ids[i]), " simple linear regression model")
print(summary(regression))
}
regression<-lm(data[["vmpfc_pos"]]~data[["vmpfc_rew"]])
summary(regression)
```


