---
title: "Behavioral Proximity Models & fMRI Activity Modulation"
author: "MW"
date: "`r Sys.Date()`"
output:
  pdf_document: default
---
### This file is compile a txt dataset that includes the evaluation and decision making activity per trial and the choice behavior.  
Notes: Made by MW on 2/12/2025. Part of the file is to create dataset holding trialwise activity based on schaefer 400 parcels, the other part for spherical ROIs. \par

dACC parcel IDs: \par
7Networks_LH_SalVentAttn_Med_1 P107 \par
7Networks_LH_SalVentAttn_Med_2 P108 \par
7Networks_LH_SalVentAttn_Med_4 P110 \par
7Networks_RH_SalVentAttn_Med_1 P311 \par
7Networks_RH_SalVentAttn_Med_2 P312 \par
For schafer parcels, I plan to first look at them separately and then combine it all together. \par
In the coged behavioral file, starting trial 46 is the first run of coged. \par

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())
#Packages; this new version won't be using boxr since I have already compile a complete dataset for coged behavioral data using CogED_MARCER_Behavior.rmd

library(lme4); library(knitr); library(rlang)
#library(boxr);
#box_auth(); 
#wustl.box <- TRUE;

options(warnPartialMatchDollar=TRUE);   # safety option
# fMRI.path <- "/scratch2/weie/COGED_CODE/np2_trial/np2trialwise/"
# out.path <-"/scratch2/weie/COGED_CODE/np2_trial/np2analysis/"
fMRI.path <- "/scratch2/weie/COGED_CODE/np2_trial/sphere_analysis/sphere_trialwise/"
out.path <-"/scratch2/weie/COGED_CODE/np2_trial/sphere_analysis/"
atlas.path <- "/data/MARCER/ATLASES/";  
dir.desc <- "20250114";  
sub.tbl <- read.table(paste0("/scratch2/weie/COGED_CODE/SubjectSet/", dir.desc, "_subjectSet.txt"), stringsAsFactors=FALSE);
sub.ids <- sub.tbl$sub.id[which(sub.tbl$COGED_CatchNonCatch == TRUE)]
# behavior.path <- box_ls('148056179835') 
behavior.path <- "/scratch2/weie/COGED_CODE/Behavioral/"
time.ids <- c("eval","dm")
# parcel.ids <- c(107,108,110,311,312)
parcel.ids <- c("VS_left", "VS_right", "vmPFC_right_Bartra", "AI_left", "AI_right", "PCC", "Brainstem", "ACC", "dACC", "SupGyr_right", "Cingulate_left", "ITG_left", "IFG_left", "IPL_left_1", "IPL_left_2", "TempPole_right", "vmPFC_right_LG", "vmPFC_left_LG", "Amygdala_right_1", "Amygdala_left", "IPS_left", "dmPFC", "IPS_right", "AI_right_Chong", "dlPFC_left", "dlPFC_right", "Insula_left", "Amygdala_right_2")
```

```{r sphere_dataset, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
#Compile a dataset with all choice behavior, proximity, and fMRI activity
# col.names <- c("subID","trial","RT","choice","Task","proximity","reward","eval.107","eval.108","eval.110","eval.311","eval.312","dm.107","dm.108","dm.110","dm.311","dm.312","eval.dACC","dm.dACC")
fixed_names <- c("subID","trial","choiceRT","choice","hardTask","proximityValue","rewardAmount")
eval_names <- paste0("eval_", parcel.ids)
dm_names <- paste0("dm_", parcel.ids)
col.names <- c(fixed_names, eval_names, dm_names)
tbl.all <- array(NA,c(36*3*length(sub.ids), length(col.names)), dimnames=list(NULL,col.names))
tbl.all[,1] <- rep(sub.ids,each = 108)
tbl.all[,2] <- rep(1:108)
behavior.data <- read.csv(paste0(behavior.path,"coged.fmri.csv"))
behavior.data <- behavior.data[behavior.data$trial>45,]
behavior.data$trial <- behavior.data$trial -45
##### I edited it til here. There must be an easier way. 
tbl.all[,(3:7)] <- as.matrix(behavior.data[,c("choiceRT","choice","hardTask","proximityValue","rewardAmount")])
for (sid in 1:length(sub.ids)) { #sid <- 1
  # file.name <- paste0("coged-MARCER-fMRI-",sub.ids[sid],"-converted.csv")
  # file.id <- box_search(file.name)
  # behavior.data <- box_read(file.id)
  # tbl.all[((sid-1)*108+1):(108*sid),(3:7)] <- as.matrix(behavior.data[46:153,c("choiceRT","choice","hardTask","proximityValue","rewardAmount")])
  for (tid in 1:length(time.ids)) { # tid<-2
    # fMRI.table <- read.delim(paste0(fMRI.path, "COGED_np2_trialwise_", time.ids[tid], "_sub", sub.ids[sid], ".txt"),header=FALSE)
    fMRI.table <- read.delim(paste0(fMRI.path, "COGED_np2_trialwise_sphere_", time.ids[tid], "_sub", sub.ids[sid], ".txt"),header=FALSE)
    tbl.all[((sid-1)*108+1):(108*sid), (length(fixed_names)+length(parcel.ids)*(tid-1)+1):(length(fixed_names)+length(parcel.ids)+length(parcel.ids)*(tid-1))] <- as.matrix(fMRI.table[,1:length(parcel.ids)])
    # tbl.all[((sid-1)*108+1):(108*sid),(18+tid-1)] <- apply(fMRI.table[,parcel.ids], 1, mean, na.rm=TRUE)
  }
}
# write.table(tbl.all,file = paste0(out.path, "COGED_trialwise_data.txt"), sep = "\t", row.names = FALSE, col.names = TRUE)
write.table(tbl.all,file = paste0(out.path, "COGED_trialwise_data_sphere.txt"), sep = "\t", row.names = FALSE, col.names = TRUE)

```

```{r schaefer_dataset, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
#####Compile a different version with everything so that we can later make a correlation with IAPS. This part of code was not on git. I ran it only on the server.
parcel.ids.all <- 1:400
fixed_names <- c("subID", "trial", "RT", "choice", "Task", "proximity", "reward")
eval_names <- paste0("eval", 1:400)
dm_names <- paste0("dm", 1:400)
col.names <- c(fixed_names, eval_names, dm_names)
tbl.all <- array(NA,c(36*3*length(sub.ids), length(col.names)), dimnames=list(NULL,col.names))
data <- read.delim(paste0(out.path, "COGED_trialwise_data.txt"), header = TRUE)
tbl.all[,1:7] <- as.matrix(data[,1:7])
for (sid in 1:length(sub.ids)) { #sid <- 1
  for (tid in 1:length(time.ids)) { # tid<-1
    fMRI.table <- read.delim(paste0(fMRI.path, "COGED_np2_trialwise_", time.ids[tid], "_sub", sub.ids[sid], ".txt"),header=FALSE)
    tbl.all[((sid-1)*108+1):(108*sid),(8+400*(tid-1)):(407+400*(tid-1))] <- as.matrix(fMRI.table[,parcel.ids.all])
  }
}
write.table(tbl.all,file = paste0(out.path, "COGED_trialwise_data_full.txt"), sep = "\t", row.names = FALSE, col.names = TRUE)
data <- read.delim(paste0(out.path, "COGED_trialwise_data_full.txt"), header = TRUE)
head(data)

######Compile a different version with reward activity (highrew-lowrew) with GLM data
out.path <- "/scratch2/weie/COGED_CODE/MW+CG_IAPSCOGED/"
atlas.path <- "/data/MARCER/ATLASES/";  
out.dirname <- paste0("/scratch2/weie/COGED_CODE/Stats/");   # top-level output directory for this particular analysis
glm.path <- "/data/MARCER/participantData/AFNI_ANALYSIS/";   # top-level input directory
subcort.tbl <- read.csv(paste0(atlas.path, "subcorticalKey.csv"), stringsAsFactors=FALSE);  # subcortical_MARCER3p0.nii.gz parcel labels
mean.eval.row <- 3:5
parcel.ids.all <- 1:400
sub.ids <- sort(sub.tbl$sub.id[which(sub.tbl[,paste0("COGED_RewardLoad")] == TRUE)]);
#Compile the empty dataset
fixed_names <- "subID"
subcort_names <- paste0(subcort.tbl$parcel.label, subcort.tbl$hemisphere)
schaefer_names <- paste0("p", parcel.ids.all)
col.names <- c(fixed_names, subcort_names, schaefer_names)
tbl.all <- array(NA,c(length(sub.ids), length(col.names)), dimnames=list(NULL,col.names))
type.ids <- c("subcortical_vol","Schaefer2018_400x7_vol")
tbl.all[,1] <- sub.ids
# Loop through both schaefer and subcortical
for (tid in 1:length(type.ids)) { #tid <-2
  for (sid in 1:length(sub.ids)) { #sid <- 1
    rewload.lbls <- c(paste0("EV_Low_", 2:4), paste0("EV_Medium_", 2:4), paste0("EV_High_", 2:4));
    rewload.lst <- vector("list", length(rewload.lbls));
    for (rid in 1:length(rewload.lbls)) { #rid <-1
      fname <- paste0(glm.path, sub.ids[sid], "/RESULTS/COGED_RewardLoad/", sub.ids[sid], "_", rewload.lbls[rid], "_", type.ids[tid], ".txt");
      if (file.exists(fname)) { rewload.lst[[rid]]  <- read.delim(fname)[-c(1,2)]; } # take off first two (label) columns
    }
    if (tid == 1) { num.cols <- 19; num.rows <- 25; do.columns <- subcort.tbl$HCP.label} 
    if (tid == 2) { num.cols <- 400; num.rows <- 25; do.columns <- 1:400} 
    for  (pid in 1:num.cols)  { # pid <- 1
      tmp.tbl <-array(NA,1:2)
      for (vid in c(2,4)) {   # vid <- 2; #When vid <- 2 and pid <-1, we are looking at the lowest reward across 3 loads in the first parcel
        inds <- which(rewload.lbls %in% c(paste0("EV_Low_", vid), paste0("EV_Medium_", vid), paste0("EV_High_", vid))); #read in all rew2
        vals.tbl <- rbind(rewload.lst[[inds[1]]][,paste0("Mean_",do.columns[pid])],
                          rewload.lst[[inds[2]]][,paste0("Mean_",do.columns[pid])],
                          rewload.lst[[inds[3]]][,paste0("Mean_",do.columns[pid])]);
        vals.reward <- apply (vals.tbl, 2, mean)
        tmp.tbl[,vid/2] <- mean(vals.reward[mean.eval.row])
      }
      Rew4_Rew2<-tmp.tbl[,2]-tmp.tbl[,1]
      if (tid == 1) {tbl.all[sid,1+pid] <- Rew4_Rew2}
      if (tid == 2) {tbl.all[sid,20+pid] <- Rew4_Rew2}
    }
  }
}
write.table(tbl.all,file = paste0(out.path, "COGED_Rew4_Rew2_Eval.txt"), sep = "\t", row.names = FALSE, col.names = TRUE)
        
        for  (pid in 1:num.cols)  { # pid <- 1
          # means for 2, 3, 4
          for (vid in 2:4) {   # vid <- 3;
            inds <- which(rewload.lbls %in% c(paste0("EV_Low_", vid), paste0("EV_Medium_", vid), paste0("EV_High_", vid)));
            vals.tbl <- rbind(rewload.lst[[inds[1]]][,paste0("Mean_",do.columns[pid])],
                              rewload.lst[[inds[2]]][,paste0("Mean_",do.columns[pid])],
                              rewload.lst[[inds[3]]][,paste0("Mean_",do.columns[pid])]);
            vals.reward <- apply (vals.tbl, 2, mean)
            # means for target knots (3-5, 10-13)
            val.reward.eval <- mean(vals.reward[mean.eval.row])
            val.reward.dec <- mean(vals.reward[mean.dec.row])
            #this needs to be changed.
            # mdd.tbl[sid*3+vid-4,4,pid] <- val.reward.eval
            # mdd.tbl[sid*3+vid-4,5,pid] <- val.reward.dec
            # mdd.tbl[sid*3+vid-4,3,pid] <- paste0("rew",vid)
            OA.tbl[sid*3+vid-4,4,pid] <- val.reward.eval
            OA.tbl[sid*3+vid-4,5,pid] <- val.reward.dec
            OA.tbl[sid*3+vid-4,3,pid] <- paste0("rew",vid)
          }
        }
      }
    }
```


```{r choice_activity, warning=FALSE, message=FALSE}
# Behavioral choice model
data <- read.delim(paste0(out.path, "COGED_trialwise_data.txt"), header = TRUE)
library(tidyverse)
install.packages("tidyverse") #Starting here I was having issue with tidyverse, so this part of code is only updated in GIT. I ran it locally.
behavior <- data[data$choice !=9, ] 
behavior$choiceCode <- ifelse(behavior$choice ==1, 1, 0) #1 is choosing easy, 2 is choosing hard. So after recoding, 1 is easy, 0 is hard.
  mutate (choiceCode = if_else(choice == 1, 1, 0),
         loadCode = factor(Task, levels = c(1,2,3), labels = c(-1,0,1)),
         rewardCode = factor(reward, levels = c(2,3,4), labels = c(-1,0,1)))
behavior$loadCode <- as.numeric(as.character(behavior$loadCode))
behavior$rewardCode <- as.numeric(as.character(behavior$rewardCode))

dm~proximity+(1|PID)
choice~eval+dm+proximity+Task+Reward+(1|PID)
```


